---
title: "DQe-c Aggregate Dashboard"
output: 
  html_document: 
    highlight: espresso
    toc: yes
---

```{r, echo=FALSE}
library("reticulate")
use_python("/anaconda/bin", required = T)
```

```{r, echo=FALSE, warning=FALSE, include=FALSE}

##processing data
require(data.table);require(dplyr);require(ggplot2);require(gridExtra);require(rmarkdown);require(knitr):require(plotly);require(DT);require(ggrepel);require(treemap)
```


```{python, echo=FALSE}

import pandas as pd
table_loads = pd.read_csv("../network_reports/05-23-2019/all_missingness_aggregation.csv")
table_loads = table_loads[table_loads["primary"]]
table_loads = table_loads[table_loads["TabNam"].isin(["person", "measurement", "condition_occurrence", "visit_occurrence"])]
```

## Network-wide changes in the main clinical tables by site and across data reload

```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width= 10, fig.height= 10, dpi= 200, fig.align='center'}

options(scipen=999)

ggplot(py$table_loads,aes(x=TEST_DATE, y = UNIQUE_FREQ, group=factor(ORGANIZATION))) +
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color=ORGANIZATION), shape = 21, size = 4, stroke= 1) + 
  geom_line(aes(color=ORGANIZATION), alpha= 0.6)+
  geom_text_repel(aes(label = ORGANIZATION))+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 2) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="none") +
  xlab("") + ylab("")
```


## A network-level preview of table availability

```{python, echo=FALSE}
import pandas as pd
table_sizes = pd.read_csv("../network_reports/05-23-2019/tablelist_aggregation.csv")

num_orgs = len(table_sizes["organization"].drop_duplicates())
    
table_sizes["count"] = table_sizes["loaded"].apply(lambda x: 1 if x else 0)
table_sizes = table_sizes[["TabNam", "count"]]

table_counts = pd.DataFrame(table_sizes.groupby(["TabNam"])["count"].sum()).reset_index()

table_counts.columns = ["TabNam", "Total"]
table_counts["size"] =1
table_counts["freq"] = table_counts["Total"]/float(num_orgs)
```


```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 5, dpi= 200, fig.align='center'}

  treemap(py$table_counts,
        index = "TabNam",
        vSize = "size",
        vColor="freq",
        type="value",
        title = "",
        title.legend = "Table availability across network",
        border.col = "white",
        position.legend = "bottom",
        range = c(0,1)
        )
```


## Network-wide missingness in available tables -- calculated from *highly* or *extremely* important columns. 
```{python, echo=FALSE}
import pandas as pd
DQ = pd.read_csv("../network_reports/05-23-2019/missingness_aggregation.csv")
DQ = DQ[(DQ["DQLVL"]=="Yes") | (DQ["DQLVL"] == "H")]
DQ["numb"] = 1
DQ_agg1 = DQ.groupby(["TabNam", "ORGANIZATION"]).agg({
    'Rows': 'mean',
    'numb': 'sum',
    'MS1_FREQ': 'sum',
    'MS2_FREQ': 'sum'})

DQ_agg1["Rows"] = DQ_agg1["Rows"] * DQ_agg1["numb"]
DQ_agg1["MSs_PERC"] = ((DQ_agg1["MS1_FREQ"] + DQ_agg1["MS2_FREQ"])/DQ_agg1["Rows"])*100

DQ_agg1.fillna(0.0, inplace=True)
DQ_agg1["perc"] = DQ_agg1["MSs_PERC"].apply(lambda x: f"{round(x, 2)}%")
DQ_agg1.drop("numb", inplace=True, axis=1)
DQ_agg1.reset_index(inplace=True)


DQ_agg2 = DQ_agg1.groupby("TabNam").agg({
    "Rows": 'sum',
    'MS1_FREQ': 'sum',
    'MS2_FREQ': 'sum'
})

DQ_agg2.reset_index(inplace=True)
DQ_agg2["MSs_PERC"] = ((DQ_agg2["MS1_FREQ"] + DQ_agg2["MS2_FREQ"])/DQ_agg2["Rows"])*100
DQ_agg2.fillna(0.0, inplace=True)
DQ_agg2["perc"] = DQ_agg2["MSs_PERC"].apply(lambda x: f"{round(x, 2)}%")
```

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 20, fig.height= 10, dpi= 300, fig.align='center'}

ggplot(py$DQ_agg2, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC),label = perc)) +
geom_point(aes(fill = MSs_PERC),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
geom_point(data=py$DQ_agg1, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC)),
            shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

scale_fill_gradient2(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
# theme_grey(base_size = base_size) +
labs(x = "", y = "") +
scale_x_continuous(limits = c(0, 1)) +
theme_minimal() +
theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
      panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
      axis.text.y=element_text(size=20, face="bold"))

```

## Column-level state of missingness across the network
```{python, echo=FALSE}
import pandas as pd
DQ = pd.read_csv("../network_reports/05-23-2019/missingness_aggregation.csv")
#DQ = DQ[(DQ["DQLVL"]=="Yes") | (DQ["DQLVL"] == "H")]

DQ_agg1 = DQ.groupby(["TabNam", "ColNam"]).agg({
    'Rows': 'mean',
    'UNIQUE_FREQ': 'sum',
    'MS1_FREQ': 'sum',
    'MS2_FREQ': 'sum'})

DQ_agg1["MSs_PERC"] = round(((DQ_agg1["MS1_FREQ"] + DQ_agg1["MS2_FREQ"])/DQ_agg1["Rows"])*100, 2)
DQ_agg1["round"] = 1
DQ_agg1.fillna(0.0, inplace=True)
DQ_agg1["perc"] = DQ_agg1["MSs_PERC"].apply(lambda x: f"{round(x*100, 2)}%")
DQ_agg1.reset_index(inplace=True)
```

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 20, fig.height= 70, dpi= 300, fig.align='center'}
ggplot(py$DQ_agg1, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC),label = perc)) +
  geom_point(data=py$DQ_agg1, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC)),
             shape = 73, colour = "black",  size = 6, alpha = 0.3) +
  geom_point(aes(color = MSs_PERC),shape = 73, size = 18,stroke=1, alpha = 1) +
  geom_text(vjust = 0.5, hjust = -0.2, nudge_y = 0, size = 4)+
  geom_label(aes(x = 1.1, label = TabNam), nudge_y = 0, size = 4)+
  scale_colour_gradient(limits=c(0, 1),low="white", high="#EE2C2C", guide=F,na.value="white", space="Lab")+
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1.1)) +
  # theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "white",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold")) +
      theme(legend.position="none") 
```
*This is ARCH Vue report*
**Vue is an add-on for DQe-c version 3.2**

**This Vue report was generated for the University of Washington on `r Sys.Date()`.**
