---
title: "DQe-c Aggregate Dashboard"
output: 
  html_document: 
    highlight: espresso
    toc: yes
---

```{r, echo=FALSE}
library("reticulate")
use_python("/anaconda/bin", required = T)
```

```{r, echo=FALSE, include=FALSE}

##processing data
require(data.table);require(dplyr);require(ggplot2);require(gridExtra);require(rmarkdown);require(knitr):require(plotly);require(DT);require(ggrepel);require(treemap)

percent = function(x, digits = 2, format = "f", ...) {
  paste0(formatC(x*100, format = format, digits = digits, ...), "%")
}
```


```{python, echo=False}

import pandas as pd
primary_table_loads = pd.read_csv("./network_reports/05-22-2019/missingness_aggregation.csv")
primary_table_loads = primary_table_loads[primary_table_loads["primary"]]

```

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 10, dpi= 200, fig.align='center'}

key.variables = py$primary_table_loads


options(scipen=999)

ggplot(key.variables,aes(x=test_date, y = UNIQFRQ, group=factor(organization))) +
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color=organization), shape = 21, size = 4, stroke= 1) + 
  geom_line(aes(color=organization), alpha= 0.6)+
  geom_text_repel(aes(label = organization))+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 2) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="none") +
  xlab("") + ylab("")

```


#A network-level preview of table availability


```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 5, dpi= 200, fig.align='center'}
count.tables.latest = as.data.frame.matrix(table(DQ.Master.latest$organization,DQ.Master.latest$TabNam))
for (i in 1:dim(count.tables.latest)[2]){
  for (j in 1:dim(count.tables.latest)[1]) {
    count.tables.latest[j,i] = ifelse(count.tables.latest[j,i] > 0, 1,count.tables.latest[j,i])
  }
}
ratio.tables.latest = data.frame(apply(count.tables.latest,2,sum)/length(unique(DQ.Master$organization)))
ratio.tables.latest$tables = row.names(ratio.tables.latest)
row.names(ratio.tables.latest) = NULL
colnames(ratio.tables.latest) = c("rate.availability","table")
ratio.tables.latest$size = 1

  treemap(ratio.tables.latest,
        index = "table",
        vSize = "size",
        vColor="rate.availability",
        type="value",
        title = "",
        title.legend = "Table availability across network",
        border.col = "white",
        position.legend = "bottom",
        range = c(0,1)
        )


```


```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 5, dpi= 200, fig.align='center'}

if (site != "network"){
  count.tables.latest.site = as.data.frame.matrix(table(DQ.Master.latest$organization,DQ.Master.latest$TabNam))
for (i in 1:dim(count.tables.latest.site)[2]){
  for (j in 1:dim(count.tables.latest.site)[1]) {
    count.tables.latest.site[j,i] = ifelse(count.tables.latest.site[j,i] > 0, 1,count.tables.latest.site[j,i])
  }
}

count.tables.latest.site = subset(count.tables.latest.site, row.names(count.tables.latest.site) == site)
ratio.tables.latest.site = data.frame(apply(count.tables.latest.site,2,sum))
ratio.tables.latest.site$tables = row.names(ratio.tables.latest.site)
row.names(ratio.tables.latest.site) = NULL
count.tables.latest.site = data.frame(count.tables.latest.site)
count.tables.latest.site$organization = as.character(row.names(count.tables.latest.site))

colnames(ratio.tables.latest.site) = c("rate.availability","table")
ratio.tables.latest.site$size = 1


  treemap(ratio.tables.latest.site,
        index = "table",
        vSize = "size",
        vColor="rate.availability",
        type="value",
        title = paste0("Table availability in ",site,"'s ",data.model," database." ),
        title.legend = "Table availability across network",
        border.col = "white",
        position.legend = "bottom",
        range = c(0,1)
        )
}

```

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 5, dpi= 200, fig.align='center'}
if (site == "network") {
ratio.sites.latest = data.frame(apply(count.tables.latest,1,sum)/length(unique(DQ.Master$TabNam)))
ratio.sites.latest$site = row.names(ratio.sites.latest)
row.names(ratio.sites.latest) = NULL
colnames(ratio.sites.latest) = c("rate.availability","site")

ratio.sites.latest$size = 1

treemap(ratio.sites.latest,
        index = "site",
        vSize = "size",
        vColor="rate.availability",
        type="value",
        title = "",
        title.legend = "Table availability by site",
        border.col = "white",
        position.legend = "bottom",
        range = c(0,1)
        )
}
```


## `r if (site == "network") {paste0("Network-wide missingness in available tables -- calculated from *highly* or *extremely* important columns.")} else if (site != "network") {paste0("Table missingness in ",site, "'s ",data.model, " (red lines), relative to the rest of the ",Net.Name," network (black and gray circles).")}` 

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 20, fig.height= 10, dpi= 300, fig.align='center'}

#subseting to important columns only
DQ.Master.latest.nonraw = subset(DQ.Master.latest,  DQ.Master.latest$DQLVL %in% c("H","X") )
DQ.Master.latest.nonraw.aggregate1 = DQ.Master.latest.nonraw  %>% 
  group_by(TabNam,organization) %>% 
  summarise(FRQ = mean(FRQ),
            # frq2 = sum(FRQ),
            numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

DQ.Master.latest.nonraw.aggregate1$FRQ = DQ.Master.latest.nonraw.aggregate1$FRQ * DQ.Master.latest.nonraw.aggregate1$numb

DQ.Master.latest.nonraw.aggregate1$MSs_PERC = (round((DQ.Master.latest.nonraw.aggregate1$MS1_FRQ+DQ.Master.latest.nonraw.aggregate1$MS2_FRQ)/DQ.Master.latest.nonraw.aggregate1$FRQ,2))
DQ.Master.latest.nonraw.aggregate1$numb = NULL
DQ.Master.latest.nonraw.aggregate1 = data.frame(DQ.Master.latest.nonraw.aggregate1)
DQ.Master.latest.nonraw.aggregate1$perc = percent(DQ.Master.latest.nonraw.aggregate1$MSs_PERC)


aggregate2x = DQ.Master.latest.nonraw.aggregate1  %>% 
  group_by(TabNam) %>% 
  summarise(FRQ = sum(FRQ),
            # numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

aggregate2x$MSs_PERC = (round((aggregate2x$MS1_FRQ+aggregate2x$MS2_FRQ)/aggregate2x$FRQ,4))
aggregate2x$organization = "network"
aggregate2x = data.frame(select(aggregate2x,TabNam,organization,FRQ,MS1_FRQ,MS2_FRQ,MSs_PERC))
aggregate2x$perc = percent(aggregate2x$MSs_PERC)

# table.site.aggregated.missingness 
tab.sit.agg.miss = rbind(DQ.Master.latest.nonraw.aggregate1, aggregate2x)

if (site == "network") {
  ggplot(aggregate2x, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC),label = perc)) +
  geom_point(aes(fill = MSs_PERC),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
  geom_point(data=DQ.Master.latest.nonraw.aggregate1, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC)),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

  scale_fill_gradient2(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
} else if (site != "network") {
  DQ.Master.latest.nonraw.aggregate1.site = subset(DQ.Master.latest.nonraw.aggregate1,
                                                   DQ.Master.latest.nonraw.aggregate1$organization == site)
  

  ggplot(aggregate2x, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC),label = perc)) +
  geom_point(aes(fill = NULL),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
      scale_fill_gradient2(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  geom_point(data=DQ.Master.latest.nonraw.aggregate1, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC)),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
      geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
    geom_point(data=DQ.Master.latest.nonraw.aggregate1.site, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC)),
             shape = 73, colour = "red",  size = 12, alpha = 1) +
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
}


```


### Changes over data reload in network-wide table missingness
```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 20, fig.height= 20, dpi= 300, fig.align='center'}

#subseting to non-raw columns only
DQ.Master.all.nonraw = subset(DQ.Master,  DQ.Master$DQLVL %in% c("H","X") )

DQ.Master.all.nonraw.aggregate = DQ.Master.all.nonraw  %>% 
  group_by(TabNam,organization,test_date) %>% 
  summarise(FRQ = mean(FRQ),
            numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

DQ.Master.all.nonraw.aggregate$FRQ = DQ.Master.all.nonraw.aggregate$FRQ * DQ.Master.all.nonraw.aggregate$numb

DQ.Master.all.nonraw.aggregate$MSs_PERC = (round((DQ.Master.all.nonraw.aggregate$MS1_FRQ+DQ.Master.all.nonraw.aggregate$MS2_FRQ)/
                                                   DQ.Master.all.nonraw.aggregate$FRQ,2))
DQ.Master.all.nonraw.aggregate$numb = NULL
DQ.Master.all.nonraw.aggregate = data.frame(DQ.Master.all.nonraw.aggregate)
DQ.Master.all.nonraw.aggregate$perc = percent(DQ.Master.all.nonraw.aggregate$MSs_PERC)

if (site == "network") {
ggplot(DQ.Master.all.nonraw.aggregate,aes(x=test_date, y = MSs_PERC, group=factor(organization)))+
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color=organization), shape = 21, size = 4, stroke= 1, guide=F) + 
  geom_line(aes(color=organization), alpha= 0.6, guide=F)+
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  geom_text_repel(aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 4) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("") #+ coord_polar(theta = "x", direction=1 )

} else if (site != "network") {

DQ.Master.all.nonraw.aggregate$site2 = ifelse(DQ.Master.all.nonraw.aggregate$organization == site, 1, 0)

ggplot(DQ.Master.all.nonraw.aggregate,aes(x=test_date, y = MSs_PERC, group=factor(organization))) +
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color = factor(site2)), shape = 21, size = 4, stroke= 3, guide=F,alpha= 0.6) + 
  geom_line(aes(color = factor(site2)), alpha= 0.6, guide=F) +
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  geom_text_repel(data= subset(DQ.Master.all.nonraw.aggregate,DQ.Master.all.nonraw.aggregate$site2 == 1),aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 4) +
  scale_colour_manual(values = c("white","red"),
                    labels = c("other sites",paste0(site)))+
theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("")
}
```




```{r, echo=FALSE, include=FALSE}
#preparing for 
DQ.Master.latest.aggregate2 = DQ.Master.latest  %>% 
  group_by(TabNam,ColNam) %>% 
  summarise(FRQ = sum(FRQ),UNIQFRQ = sum(UNIQFRQ),MS1_FRQ = sum(MS1_FRQ),MS2_FRQ = sum(MS2_FRQ))

DQ.Master.latest.aggregate2$MSs_PERC = (round((DQ.Master.latest.aggregate2$MS1_FRQ+
                                                 DQ.Master.latest.aggregate2$MS2_FRQ)/DQ.Master.latest.aggregate2$FRQ,2))


DQ.Master.latest.aggregate2$test_date = as.character(format(Sys.Date(),"%m-%d-%Y"))
DQ.Master.latest.aggregate2$organization = "network"
DQ.Master.latest.aggregate2$round = 1
DQ.Master.latest.aggregate2$perc = percent(DQ.Master.latest.aggregate2$MSs_PERC)

# 
DQ.Master.latest$perc = percent(DQ.Master.latest$MSs_PERC)
##############
##############
###############
if (site != "network") { 
  DQ.Master.latest.site = subset(DQ.Master.latest, DQ.Master.latest$organization == site)
  DQ.Master.latest.site$perc = percent(DQ.Master.latest.site$MSs_PERC)
  }
```


## `r if (site == "network") {paste0("Column-level state of missingness across the network")} else if (site != "network") {paste0("Column missingness in ",site, "'s ",data.model, " (red lines) tables, relative to the rest of the ",Net.Name," network (gray lines)")}` 

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 20, fig.height= 70, dpi= 300, fig.align='center'}
if (site == "network") { 

ggplot(DQ.Master.latest.aggregate2, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC),label = perc)) +
  geom_point(data=DQ.Master.latest, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC)),
             shape = 73, colour = "black",  size = 6, alpha = 0.3) +
  geom_point(aes(color = MSs_PERC),shape = 73, size = 18,stroke=1, alpha = 1) +
  geom_text(vjust = 0.5, hjust = -0.2, nudge_y = 0, size = 4)+
  geom_label(aes(x = 1.1, label = TabNam), nudge_y = 0, size = 4)+
  scale_colour_gradient(limits=c(0, 1),low="white", high="#EE2C2C", guide=F,na.value="white", space="Lab")+
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1.1)) +
  # theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "white",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold")) +
      theme(legend.position="none") 
  } else if (site != "network") { 
    
  ggplot(DQ.Master.latest.aggregate2, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC),label = perc)) +
  geom_point(data=DQ.Master.latest, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC)),
             shape = 73, colour = "black",  size = 6, alpha = 0.3) +
  geom_point(color = "black",shape = 73, size = 18,stroke=1, alpha = 0.5) +
  geom_text(vjust = 0.5, hjust = -0.2, nudge_y = 0, size = 4)+
  geom_label(aes(x = 1.1, label = TabNam), nudge_y = 0, size = 4)+
  scale_colour_gradient(limits=c(0, 1),low="white", high="black", guide=F,na.value="white", space="Lab")+
  geom_point(data=DQ.Master.latest.site, aes(x=MSs_PERC,y=reorder(ColNam,-MSs_PERC)),
             shape = 73, colour = "red",  size = 10, alpha = 0.9) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1.1)) +
  # theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "white",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"),
        legend.position="none") 
}


```


## `r if (site == "network") {paste0("Network-wide missingness in key indicators")} else if (site != "network") {paste0("Key variable missingness in ",site, "'s ",data.model, " (red lines), relative to the rest of the ",Net.Name," network (black and gray circles)")}` 

```{r, echo=FALSE, include=FALSE}

###with
without.names = report.tables[(report.tables$table.group == "without"),"table.names"]
without.tabs = list()
for (w in 1:length(without.names)) {
  without.tabs[[w]] = data.frame(read.csv(paste0(pth,"/",without.names[w])))
}

withouts.network = do.call(rbind, lapply(without.tabs, data.frame, stringsAsFactors=FALSE))
rm(without.tabs)

withouts.network$missing.population = round((withouts.network$missing.percentage/100)*withouts.network$denominator,0)

withouts.network$missing.ratio = withouts.network$missing.percentage/100


withouts.network$test_date = as.Date(withouts.network$test_date, format = "%m-%d-%Y")
withouts.network = merge(withouts.network,DQ.rounds, by=c("organization","test_date"), all.x = TRUE)

##temporarily 
withouts.network = subset(withouts.network, !(withouts.network$group %in% c("encounter","diagnosis","medication")))
####

latest.withouts.network = aggregate(withouts.network$test_date, by = list(withouts.network$organization), max)
latest.withouts.network$run.char = paste0(latest.withouts.network$Group.1,latest.withouts.network$x)
withouts.network$round.x = withouts.network$round
latest.withouts.network.round = aggregate(withouts.network$round, by = list(withouts.network$organization), max)
latest.withouts.network.round$round.char = paste0(latest.withouts.network.round$Group.1,latest.withouts.network.round$x)

withouts.network$run.char = paste0(withouts.network$organization,withouts.network$test_date)
withouts.network$round.char = paste0(withouts.network$organization,withouts.network$round)

# subseting the latest withouts table
withouts.network.latest = select(subset(withouts.network,withouts.network$run.char %in% c(latest.withouts.network$run.char)),group,missing.percentage,missing.population,denominator,perc,organization,test_date, missing.ratio)
                                 
# 
withouts.network.latest.aggregate = withouts.network.latest %>% group_by(group) %>% summarise(missing.pop = sum(missing.population),denominator = sum(denominator))

# 
withouts.network.latest.aggregate$missing.ratio = round((withouts.network.latest.aggregate$missing.pop/withouts.network.latest.aggregate$denominator),4)
withouts.network.latest.aggregate$perc = percent(withouts.network.latest.aggregate$missing.ratio)
withouts.network.latest.aggregate$organization = "network"
withouts.network.latest.aggregate$test_date = as.character(format(Sys.Date(),"%m-%d-%Y"))
```


```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 20, fig.height= 10, dpi= 300, fig.align='center'}

if (site == "network") {
ggplot(withouts.network.latest.aggregate, aes(x=missing.ratio,y=reorder(group,-missing.ratio),
                                              label = perc)) +
  geom_point(aes(fill = missing.ratio),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
  geom_point(data=withouts.network.latest, aes(x=missing.ratio,y=reorder(group,-missing.ratio)),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
} else if (site != "network") {
  
  withouts.network.latest.site = subset(withouts.network.latest, withouts.network.latest$organization == site)


  ggplot(withouts.network.latest.aggregate, aes(x=missing.ratio,y=reorder(group,-missing.ratio),
                                              label = perc)) +
  geom_point(aes(fill = NULL),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.8) +
  geom_point(data=withouts.network.latest, aes(x=missing.ratio,y=reorder(group,-missing.ratio)),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
   geom_point(data=withouts.network.latest.site, aes(x=missing.ratio,y=reorder(group,-missing.ratio)),
             shape = 73, colour = "red",  size = 12, alpha = 0.9) +
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
  
}

```


### Changes over data reload in network-wide missingness in key indicators

```{r, echo=FALSE,warning = FALSE, fig.align='center', fig.width= 20, fig.height= 15, dpi= 300, fig.align='center'}

if (site == "network") {
ggplot(withouts.network,aes(x=test_date, y = missing.percentage, group=factor(organization)))+
  geom_point(aes(color=organization), shape = 21, size = 4, stroke= 1, guide=F) + 
  geom_line(aes(color=organization), alpha= 0.6, guide=F)+
  geom_text_repel(aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ group, scale="free_y", ncol = 5) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("") #+ coord_polar(theta = "x", direction=1 )
} else if (site != "network") {
  
  withouts.network$site2 = ifelse(withouts.network$organization == site, 1, 0)
  
  ggplot(withouts.network,aes(x=test_date, y = missing.percentage, group=factor(organization)))+
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color = factor(site2)), shape = 21, size = 4, stroke= 3, guide=F) + 
  geom_line(aes(color = factor(site2)), alpha= 0.6, guide=F)+
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  geom_text_repel(data = subset(withouts.network,withouts.network$site2 == 1),aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ group, scale="free_y", ncol = 5) +
  scale_colour_manual(values = c("white","red"),
                    labels = c("other sites",paste0(site)))+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("")
  
}


```



*This is ARCH Vue report*
**Vue is an add-on for DQe-c version 3.2**

**This Vue report was generated for `r if (site == "network") {paste0(Net.Name," Network")} else if (site != "network") {paste0(site," organization")}` on `r Sys.Date()`.**
