---
title: "DQe-c-v2 Report"
output: 
  html_document: 
    highlight: tango
params:
  config: "config.json"
  outputDir: "report"
---

```{r, echo=FALSE}
library("reticulate")
#use_python("/anaconda/bin", required = T)
use_condaenv()
config = params$config
outputDir = params$outputDir
```

```{python, echo=FALSE}
import json

config = r.config
outputDir = r.outputDir

config = json.load(open(config))

CDM = config["CDM"].upper()

if CDM == "":
        raise NameError(f"A Common Data Model (CDM) has not been defined in config file")
elif CDM not in ["PCORNET3","PCORNET31","OMOPV5_0","OMOPV5_2","OMOPV5_3"]:
        raise NameError(f"{CDM} is not a valid Common Data Model")

organization = config["Organization"]
```

```{r, echo=FALSE, include=FALSE}
CDM = py$CDM
ORGANIZATION = py$organization
```


## Load and Test Details

This DQec report is generated from testing completeness in `r CDM` data from `r ORGANIZATION` on `r Sys.Date()`. 

### Table 1. List and Status of Common Data Model (CDM) -- here, `r CDM` -- Tables in this load
The table below provides a list of CDM tables provided (and not provided) in the data load.

The source data this table and the following graphics in this section are being generated from is reports/`r ORGANIZATION`/`r Sys.Date()`/tablelist.csv

```{r, echo=FALSE, fig.align='center', fig.width= 10}
dato <- read.csv(paste(py$outputDir, "tablelist.csv", sep=""))
dato$TotalSizeKB <- ifelse(is.null(dato$TotalSizeKB) | is.na(dato$TotalSizeKB), 0, dato$TotalSizeKB)
dato$TotalSizeGB <- round(as.numeric(dato$TotalSizeKB)/1000000,4)
dato$Rows <- ifelse(is.null(dato$Rows) | is.na(dato$Rows), 0, dato$Rows)
dato$status <- ifelse((dato$loaded == "True"), "Table available", "Table not available")
dato$status[(dato$Rows == 0) & (dato$loaded == "True")] <- "Table empty"
dato$vSize <- rep(1,nrow(dato))

#sub_dato <- subset(dato,primary=="TRUE")
sub_dato <- distinct(dato,dato$TabNam, .keep_all = TRUE)
datatable(select(sub_dato, TabNam, status, TotalSizeGB, Rows), options = list(pageLength = 5), filter = 'bottom')
```

### Figure 1. Available Tables, Compared to all CDM (`r CDM`) Tables
This figure shows which of the CDM tables are loaded and/or available. 

```{r, echo=FALSE, fig.align='center', fig.width= 10}
treemap(sub_dato,
        index=c("TabNam"),
        vSize="vSize",
        vColor="status",
        type="categorical",
        title = "",
        title.legend = "Table Availability",
        border.col = "white",
        position.legend = "bottom"
        )
```

### Figure 2. File Size and Row Numbers by Table in the (`r CDM`) Load
```{r, echo=FALSE, fig.align='center', fig.width= 12}
treemap(sub_dato,
        index=c("TabNam"),
        vSize="Rows",
        vColor="TotalSizeGB",
        type="value",
        title = "",
        title.legend = "Size represents number of rows and color represent file size (in GB) for each table.",
        border.col = "white",
        position.legend = "bottom"
)
```

```{python, echo=FALSE}
import pandas as pd
from typing import List

DQTBL: object = pd.read_csv(r.outputDir + "tablelist.csv")

primaryPairs: object = DQTBL[DQTBL["primary"] == True][["ColNam", "TabNam"]]
referencePairs: object = DQTBL[DQTBL["primary"] == False][["ColNam", "TabNam"]]

referencePrimaryMerge: object = primaryPairs.merge(referencePairs, on="ColNam", how="right", suffixes=("_primary", "_reference"))
referencePrimaryMerge.dropna(subset = ["TabNam_primary"], inplace=True)

id=[]
id_dict={}
from_ind=[]
to_ind=[]
stat=[]

prim=referencePrimaryMerge.TabNam_primary
ref=referencePrimaryMerge.TabNam_reference
comb=prim.append(ref, ignore_index=True).unique()

for i in range(0,len(comb)):
        id_dict[comb[i]]=i
        stat.append("Table available") if (DQTBL[DQTBL["TabNam"]==comb[i]]["loaded"].unique()[0]==True) else stat.append("Table not available")
        
for i in range(0,len(id_dict)):
        id.append(i)

for _,row in referencePrimaryMerge.iterrows():
        from_ind.append(id_dict[row['TabNam_primary']])
        to_ind.append(id_dict[row['TabNam_reference']])

label = list(id_dict.keys())
```

### Figure 3. Loaded tables against CDM (`r CDM`) Relational Model.
The figure below shows a network visualization of the CDM data model, as well as highlighting the tables that are available in this load (legend is the same as in Figure 1).

```{r, echo=FALSE, fig.align='center', fig.width= 10}
dat.net <- py$referencePrimaryMerge

nodes <- data.frame(id = py$id, 
                  label = py$label,
                  group = py$stat,
                  #shadow = c(FALSE)
                  shadow = F) # if OMOP, shadow = F 
edges <- data.frame(from = py$from_ind, to = py$to_ind)
visNetwork(nodes, edges) %>%

visGroups(groupname = "Table not available", color = "#00C5CD", shape = "circle") %>%
visGroups(groupname = "Table available", color = "#EE9572", shape = "circle") %>%

visOptions(highlightNearest = TRUE, nodesIdSelection = T) %>% 
visEdges(arrows = 'from', scaling = list(min = .5, max = 1)) %>%
visInteraction(navigationButtons = T, dragView = FALSE, zoomView = FALSE)

```


## Completeness Results
### Table 2. The Master Completeness Results Table
The table below provides results of completeness test at the value/cell level.

* `TabNam` = `r CDM`  table name
* `ColNam` = Column name
* `DQLVL` = Level of importance for completeness test. (`X`: Extremely Important, `H`: Highly Important, `L`:Low Importance)
* `FREQ` = Frequency of rows
* `UNIQUE_FREQ` = Frequency of unique values in each column
* `MS1_FREQ` = Frequency of cells with NULL/NA values or empty strings in each column
* `MS2_FREQ` = Frequency of cells with characters in each column that don't represent meaningful data -- including, '+', '-', '_','#', '$', '*', '\', '?', '.', '&', '^', '%', '!', '@', and 'NI'.
* `MSs_PERCENTAGE` = Percentage of overall missing data in each column 
Data for this table is generated from `r paste("DQ_Master_Table_",CDM,"_",ORGANIZATION,"_",as.character(format(Sys.Date(),"%d-%m-%Y")),".csv", sep="")` saved under report directory.

```{r, echo=FALSE}
DQTBL <- read.csv(paste(py$outputDir, "missingness.csv", sep=""))
datatable(DQTBL[,c("TabNam","ColNam","DQLVL", "Rows", "UNIQUE_FREQ","MS1_FREQ","MS2_FREQ","MSs_PERCENTAGE", "TEST_DATE")], options = list(pageLength = 10), filter = 'bottom')
```

### Figure 4. Changes in Primary Keys Across Loads
Figure below profiles changes in primary keys across loads as a measure of change in patient/record number over time.

```{python, echo=FALSE, warning=FALSE, message=FALSE}
import pandas as pd
import os

report_directory = "/".join(r.outputDir.split("/")[:-2])
prim_loads = pd.DataFrame()

for folder in os.listdir(report_directory):
  if folder.startswith('.'):
    pass
  else:
    data = pd.read_csv(report_directory + "/" + folder + "/missingness.csv")
    data = data[data["cat"]!="vocabulary"]
    data = data[data["primary"]]
    data = data[["TabNam","ColNam", "UNIQUE_FREQ", "TEST_DATE"]]
    prim_loads = prim_loads.append(data)
```

```{r, echo=FALSE, warning=FALSE,  message=FALSE, fig.align='center', fig.height= 10,  fig.width= 10}
ggplot(py$prim_loads, aes(x=reorder(TEST_DATE,TEST_DATE), y=UNIQUE_FREQ, group = ColNam) ) + 
  geom_line(aes(), alpha = 0.4,  size = 1, show.legend = FALSE) + 
  stat_smooth(colour = "red",level=0.99) +
  geom_point( alpha = 0.5, shape = 1, size = 6, colour = "#FF3333", stroke = 2, show.legend = FALSE) + 
  geom_point( aes(col = TEST_DATE), shape = 20, size = 8,   show.legend = T) + 
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", hjust=0)) +
  xlab("Load") + ylab("Unique Counts") + 
  facet_wrap(~TabNam, ncol = 3, strip.position = "bottom", scales = "free") +
  theme(axis.text.x=element_text(colour="white", size = 0.1))
```

### Figure set 1. Proportion of Missing Data by Type in Loaded Tables
Figures below show proportion of missing cells/values in each column of each table loaded. Figures are generated based on Table 2. 

* `MS1_FREQ` = Frequency of cells with NULL/NA values and empty strings in each column -- presence of absence
* `MS2_FREQ` = Frequency of cells with characters in each column that don't represent meaningful data -- presence of nonsense 


```{r, echo=FALSE, ggplot, warning=FALSE,  message=FALSE, fig.align='center', fig.height= 5, fig.width= 12}
DQTBL$MS1_PERC <- ifelse(DQTBL$Rows == 0, 0, round((DQTBL$MS1_FREQ)/DQTBL$Rows,2))
DQTBL$MS2_PERC <- ifelse(DQTBL$Rows == 0, 0, round((DQTBL$MS2_FREQ)/DQTBL$Rows,2))
DF <- subset(melt(DQTBL, id.var=c("TabNam","ColNam")), variable %in% c("MS1_PERC","MS2_PERC"))
DF$value <- as.numeric(DF$value)
colnames(DF)[3] <- "DQ_Issue"
colnames(DF)[4] <- "Ratio"
#####plotting
plot_list<- list()
table_list <- unique(DQTBL$TabNam)
# create for loop to produce ggplot2 graphs 
for (i in seq_along(table_list)) { 
  
  # create plot for each OMOP table in DQTBL 
  plot_list[[i]] <- 
    plot_list[[i]] <- 
    ggplot(subset(DF, TabNam==table_list[i]),
           aes(x=ColNam, y=Ratio, fill=DQ_Issue)) + 
    geom_bar(stat="identity", width = 1) +
    #     scale_fill_manual(values=c("red","green","orange","dark red")) +
    facet_wrap( ~ ColNam, scale="free_x", nrow = 1) +
    #     ggtitle("Frequency of Missing Data") +
    xlab("Column") +
    ylab("Frequency") +
    theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", hjust=0),
          axis.text.x = element_text(vjust = 1),
          strip.text.x = element_text(angle = 90, face="bold")) +
    theme(axis.text.x=element_blank())+    # theme(legend.position="none") + 
    ggtitle(paste('Ratio of Missing Data in "', table_list[i], '" table', sep=''))
  
}
plot_list
```

## Data Model Tests

### Figure set 2. Common Key Variables
Figures below visualize number of unique key variables that are common in multiple `r CDM` tables. 

* The Reference column on the right comes from the table in which the variable is a primary key, and therefore is a reference for all other tables. 

* Count_Out shows number of unique key variables that are not present in the reference table -- e.g., person id from observation table that does not exist in person table.

* Count_In represent number of unique key variables that are present in the reference table -- e.g., person id from observation table that exist in person table as well.

```{r, echo=FALSE,  fig.align='center', fig.height= 3, fig.width= 10}
plot_list<- list()
ORPHAN <- read.csv(paste(py$outputDir, "orphan.csv", sep=""))
KEYS <- unique(ORPHAN$ColNam)
for (i in seq_along(KEYS)) {

  prim_col<- filter(ORPHAN, ColNam == KEYS[i])
  
  plot_list[[i]] <- ggplot(data=prim_col, aes(x=reorder(TabNam, UNIQUE_FREQ), y=UNIQUE_FREQ)) +
  geom_bar(stat="identity", width = 1, aes(fill=Index)) +
  scale_fill_manual(values=c("darkolivegreen3","firebrick1", "springgreen3")) +
  ggtitle(paste("Count of Unique ",unique(prim_col$ColNam)," in Tables with ",unique(prim_col$ColNam),
                sep="")) +
  xlab(" Table Name") +
  ylab("Frequency of Unique Values")
}
plot_list
```

## Test of Completeness in Key Clinical Indicators

### Figure 5. Common Key Variables
Figure 5 shows the percentage of patients missing specific key clinical indicators. 

```{r, echo=FALSE, fig.align='center', fig.height= 5, fig.width= 10}
withouts <- read.csv(paste(py$outputDir, "indicators.csv", sep=""))
  
ggplot(withouts, aes(x=MISSING_PERCENTAGE,y=reorder(GROUP,-MISSING_PERCENTAGE), label = PERCENTAGE)) + 
    geom_point(aes(fill = MISSING_PERCENTAGE),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
    geom_text(vjust = -0.5, hjust = -.38, nudge_y = 0, size = 4)+
    scale_fill_gradient(limits=c(0, 100),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
    labs(x = "", y = "") +
    scale_x_continuous(limits = c(0, 100)) +
    theme_minimal() +
    theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
          panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
          axis.text.y=element_text(size=20, face="bold"))
```

## Demographics visualization

```{r, echo=FALSE, fig.align='center', fig.width= 10}
library(ggplot2)
library(tidyverse)
demog <- read.csv("path/to/demographic.csv")
cols=colnames(demog)
temp=c()
for (ind in c(1:length(cols))){temp=c(temp,demog[[cols[ind]]])}
demog=data.frame(xval=colnames(demog),yval=temp)

gender=demog[2:3,]
ggplot(data=gender, aes(xval,yval,fill=factor(xval)))
  + geom_bar(stat="identity", width=0.4)
  + xlab("Gender")
  + ylab("Total Count")
  + labs(fill="Gender")
  + coord_flip()

ethnicity=demog[4:5,]
ggplot(data=ethnicity, aes(xval,yval,fill=factor(xval)))
  + geom_bar(stat="identity", width=0.4)
  + xlab("Ethnicity")
  + ylab("Total Count")
  + labs(fill="Ethnicity")
  + coord_flip()

race=demog[6:nrow(demog),]
race %>% mutate(xval=fct_reorder(xval, desc(yval))) %>% ggplot(aes(xval,yval,fill=factor(xval)))
  + geom_bar(stat="identity", width=0.4)
  + xlab("Race")+ ylab("Total Count")
  + labs(fill="Race")
  + coord_flip()

ggplot(race, aes(x=xval,y=yval,size=seq(min(yval),max(yval),length.out=length(yval)),color=xval))+geom_point()
```